Adaptive broadcast tree for multicores

### 2013-04-29 paper.tex
Added some information on gruyere (which is the machine we base our sample model on)

\subsection{Example}

An example of a machine model, which approximates a 2x2x1 nos box can
be found in Figure~\ref{fig:full_nos}

\begin{figure}
\begin{tikzpicture}[>=latex,line join=bevel]
  \pgfsetlinewidth{1bp}
\input{graphs/full_nos}
\end{tikzpicture}
\caption{Network model of a 2x2x1 machine}
\label{fig:full_nos}
\end{figure}

@@

An important variable in constructing such a tree is the degree of
nodes. If the send cost $t_s$ is smaller than the propagation time
$t_p$,  $d = \lceil \frac{t_p}{t_s} \rceil$ messages can be send to
hide propagation of messages. Hence, a tree with degree $d$ should be
ideal to minimize latency, but only for an acknowledged protocol.

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{graphs/visu}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores.}
  \label{fig:mst_gruyere_operations}
\end{figure}

>>>>

\subsubsection{Example model approximating a 8x4x1 machine}

We now make up a machine model for evaluation. This model is based on
a 8x4x1 AMD Shanghai machine. The topology of such a machine is shown
in Figure~\ref{fig:gruyere}.

Each of the eight nodes consists of four cores. We approximate the
cost of sending messages within nodes as $1$ and across nodes as
$10*num(hops)$.

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[
    xscale=.7,
    yscale=.5,
    every node/.style={draw,fill=red!10,minimum width=2cm,minimum height=1cm}
    ]
    \node (c1) at ( 0, 4) {node 0};
    \node (c2) at ( 4, 4) {node 1};
    \node (c3) at ( 8, 4) {node 2};
    \node (c4) at (12, 4) {node 3};

    \node (c5) at ( 0, 0) {node 4};
    \node (c6) at ( 4, 0) {node 5};
    \node (c7) at ( 8, 0) {node 6};
    \node (c8) at (12, 0) {node 7};

    % top horizontal
    \draw[thick] (c1) -- (c2);
    \draw[thick] (c2) -- (c3);
    \draw[thick] (c3) -- (c4);
    % bottom horizontal
    \draw[thick] (c5) -- (c6);
    \draw[thick] (c6) -- (c7);
    \draw[thick] (c7) -- (c8);
    % vertical
    \draw[thick] (c1) -- (c5);
    \draw[thick] (c2) -- (c6);
    \draw[thick] (c3) -- (c7);
    \draw[thick] (c4) -- (c8);
    % cross
    \draw[thick] (c3) -- (c8);
    \draw[thick] (c4) -- (c7);
  \end{tikzpicture}
  \caption{Interconnect topology of 8x4x1 AMD Shanghai machine}
  \label{fig:gruyere}
\end{figure}

@@

An important variable in constructing such a tree is the degree of
nodes. If the send cost $t_s$ is smaller than the propagation time
$t_p$,  $d = \lfloor \frac{t_p}{t_s} \rfloor$ messages can be send to
hide propagation of messages. Hence, a tree with degree $d$ should be
ideal to minimize latency, but only for an acknowledged protocol.

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_only_mst}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores. The
    tree has been acquired using an MST algorithm.}
  \label{fig:mst_gruyere_operations}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_mst_sort}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores. After
    running the MST algorithm, we optimize scheduling in every node to
    send messages to in decreasing order of their latency.}
  \label{fig:mst_gruyere_operations_sorted}
\end{figure}
